Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2021-09-20 ch-abm.tex
Add supplemental results.

Here we present the results of 1000 runs of an agent-based model of deliberation.
In each run, an NK model is generated (N=15, K=6) and the model is simulated for 300
iterations for each network/strategy combination.
The results of these simulations are shown in Figure \ref{fig:results}.

@@

>>>>

Here we present the results of 1000 runs of an agent-based model of deliberation.
In each run, an NK model is generated (N=15, K=6) and the model is simulated for 300
iterations for each network/strategy combination.
The results of these simulations are shown in Figure \ref{fig:results}.
Figures \ref{fig:results-frac-parallel} and \ref{fig:results-frac-fallback} show pairwise comparisons of solution quality between strategy/network settings. Figures \ref{fig:results-bn-parallel-dist}--\ref{fig:results-conf-fallback-dist} show the complete solution quality distributions for all settings.
Tables \ref{tab:t-instrat-fallback}--\ref{tab:t-innet-parallel} show the t-values and Bonferroni-corrected p-values for comparisons across networks and strategies.

@@

\begin{figure}
    \label{fig:results-frac-parallel}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for parallel individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-frac-fallback}
    \centering
%    \includegraphics[width=3.33in]{fig/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for fallback individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-bn-parallel-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-cn-parallel-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-conf-parallel-dist.eps}
\caption{Solution quality distribution for the conform strategy with parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-bn-fallback-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-cn-fallback-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{fig/NetDelibABM/results-conf-fallback-dist.eps}
\caption{Solution quality distribution for the conform strategy with fallback individual learning.}
\end{figure}

\begin{table*}[]
    \label{tab:t-instrat-fallback}
    \centering
    \begin{tabular}{l|ll|ccc}
        Strategy & Net A & Net B & $\overline{B - A}$ & t & p* \\
        \hline
Best Neighbor&Pref. Attach.&Small World&-8.70e-02&-1.33e+01&1.27e-35\\
Best Neighbor&Pref. Attach.&Long Path&-5.98e-02&-8.62e+00&1.51e-15\\
Best Neighbor&Pref. Attach.&Random Pod&-1.15e-02&-1.83e+00&4.01e+00\\
Best Neighbor&Small World&Pref. Attach.&8.70e-02&1.33e+01&1.27e-35\\
Best Neighbor&Small World&Long Path&2.72e-02&4.53e+00&3.88e-04\\
Best Neighbor&Small World&Random Pod&7.55e-02&1.18e+01&1.66e-28\\
Best Neighbor&Long Path&Pref. Attach.&5.98e-02&8.62e+00&1.51e-15\\
Best Neighbor&Long Path&Small World&-2.72e-02&-4.53e+00&3.88e-04\\
Best Neighbor&Long Path&Random Pod&4.83e-02&7.34e+00&2.69e-11\\
Best Neighbor&Random Pod&Pref. Attach.&1.15e-02&1.83e+00&4.01e+00\\
Best Neighbor&Random Pod&Small World&-7.55e-02&-1.18e+01&1.66e-28\\
Best Neighbor&Random Pod&Long Path&-4.83e-02&-7.34e+00&2.69e-11\\
\hline
Confident Neighbor&Pref. Attach.&Small World&-7.52e-02&-1.13e+01&2.94e-26\\
Confident Neighbor&Pref. Attach.&Long Path&2.39e-03&3.64e-01&4.30e+01\\
Confident Neighbor&Pref. Attach.&Random Pod&5.80e-02&8.88e+00&1.86e-16\\
Confident Neighbor&Small World&Pref. Attach.&7.52e-02&1.13e+01&2.94e-26\\
Confident Neighbor&Small World&Long Path&7.76e-02&1.21e+01&1.08e-29\\
Confident Neighbor&Small World&Random Pod&1.33e-01&1.92e+01&1.36e-68\\
Confident Neighbor&Long Path&Pref. Attach.&-2.39e-03&-3.64e-01&4.30e+01\\
Confident Neighbor&Long Path&Small World&-7.76e-02&-1.21e+01&1.08e-29\\
Confident Neighbor&Long Path&Random Pod&5.56e-02&8.50e+00&4.00e-15\\
Confident Neighbor&Random Pod&Pref. Attach.&-5.80e-02&-8.88e+00&1.86e-16\\
Confident Neighbor&Random Pod&Small World&-1.33e-01&-1.92e+01&1.36e-68\\
Confident Neighbor&Random Pod&Long Path&-5.56e-02&-8.50e+00&4.00e-15\\
\hline
Conform&Pref. Attach.&Small World&3.60e-02&6.78e+00&1.24e-09\\
Conform&Pref. Attach.&Long Path&-1.63e-01&-2.22e+01&2.25e-87\\
Conform&Pref. Attach.&Random Pod&-2.28e-01&-3.19e+01&9.08e-153\\
Conform&Small World&Pref. Attach.&-3.60e-02&-6.78e+00&1.24e-09\\
Conform&Small World&Long Path&-1.99e-01&-3.17e+01&1.59e-151\\
Conform&Small World&Random Pod&-2.64e-01&-4.43e+01&2.20e-236\\
Conform&Long Path&Pref. Attach.&1.63e-01&2.22e+01&2.25e-87\\
Conform&Long Path&Small World&1.99e-01&3.17e+01&1.59e-151\\
Conform&Long Path&Random Pod&-6.48e-02&-8.31e+00&1.79e-14\\
Conform&Random Pod&Pref. Attach.&2.28e-01&3.19e+01&9.08e-153\\
Conform&Random Pod&Small World&2.64e-01&4.43e+01&2.20e-236\\
Conform&Random Pod&Long Path&6.48e-02&8.31e+00&1.79e-14\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across networks, within strategies. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}

\begin{table*}[]
    \label{tab:t-innet-fallback}
    \centering
    \begin{tabular}{l|ll|ccc}
        Network & Strategy A & Strategy B & $\overline{B - A}$ & t & p* \\
        \hline
Pref. Attach.&Best Neighbor&Confident Neighbor&-6.43e-02&-9.39e+00&2.33e-18\\
Pref. Attach.&Best Neighbor&Conform&8.96e-02&1.19e+01&6.83e-29\\
Pref. Attach.&Confident Neighbor&Best Neighbor&6.43e-02&9.39e+00&2.33e-18\\
Pref. Attach.&Confident Neighbor&Conform&1.54e-01&2.06e+01&7.57e-77\\
Pref. Attach.&Conform&Best Neighbor&-8.96e-02&-1.19e+01&6.83e-29\\
Pref. Attach.&Conform&Confident Neighbor&-1.54e-01&-2.06e+01&7.57e-77\\
\hline
Small World&Best Neighbor&Confident Neighbor&-5.26e-02&-8.39e+00&9.70e-15\\
Small World&Best Neighbor&Conform&2.13e-01&3.52e+01&4.46e-175\\
Small World&Confident Neighbor&Best Neighbor&5.26e-02&8.39e+00&9.70e-15\\
Small World&Confident Neighbor&Conform&2.65e-01&4.45e+01&1.24e-237\\
Small World&Conform&Best Neighbor&-2.13e-01&-3.52e+01&4.46e-175\\
Small World&Conform&Confident Neighbor&-2.65e-01&-4.45e+01&1.24e-237\\
\hline
Long Path&Best Neighbor&Confident Neighbor&-2.12e-03&-3.42e-01&4.39e+01\\
Long Path&Best Neighbor&Conform&-1.37e-02&-1.71e+00&5.20e+00\\
Long Path&Confident Neighbor&Best Neighbor&2.12e-03&3.42e-01&4.39e+01\\
Long Path&Confident Neighbor&Conform&-1.16e-02&-1.44e+00&8.96e+00\\
Long Path&Conform&Best Neighbor&1.37e-02&1.71e+00&5.20e+00\\
Long Path&Conform&Confident Neighbor&1.16e-02&1.44e+00&8.96e+00\\
\hline
Random Pod&Best Neighbor&Confident Neighbor&5.18e-03&8.40e-01&2.41e+01\\
Random Pod&Best Neighbor&Conform&-1.27e-01&-1.64e+01&1.07e-51\\
Random Pod&Confident Neighbor&Best Neighbor&-5.18e-03&-8.40e-01&2.41e+01\\
Random Pod&Confident Neighbor&Conform&-1.32e-01&-1.67e+01&1.39e-53\\
Random Pod&Conform&Best Neighbor&1.27e-01&1.64e+01&1.07e-51\\
Random Pod&Conform&Confident Neighbor&1.32e-01&1.67e+01&1.39e-53\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across strategies, within networks. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}

\begin{table*}[]
    \label{tab:t-instrat-parallel}
    \centering
    \begin{tabular}{l|ll|ccc}
        Strategy & Net A & Net B & $\overline{B - A}$ & t & p* \\
    \hline
Best Neighbor&Pref. Attach.&Small World&-6.75e-02&-1.13e+01&2.48e-26\\
Best Neighbor&Pref. Attach.&Long Path&-4.24e-02&-6.78e+00&1.25e-09\\
Best Neighbor&Pref. Attach.&Random Pod&-8.14e-03&-1.32e+00&1.12e+01\\
Best Neighbor&Small World&Pref. Attach.&6.75e-02&1.13e+01&2.48e-26\\
Best Neighbor&Small World&Long Path&2.50e-02&4.25e+00&1.42e-03\\
Best Neighbor&Small World&Random Pod&5.93e-02&9.38e+00&2.54e-18\\
Best Neighbor&Long Path&Pref. Attach.&4.24e-02&6.78e+00&1.25e-09\\
Best Neighbor&Long Path&Small World&-2.50e-02&-4.25e+00&1.42e-03\\
Best Neighbor&Long Path&Random Pod&3.43e-02&5.36e+00&6.14e-06\\
Best Neighbor&Random Pod&Pref. Attach.&8.14e-03&1.32e+00&1.12e+01\\
Best Neighbor&Random Pod&Small World&-5.93e-02&-9.38e+00&2.54e-18\\
Best Neighbor&Random Pod&Long Path&-3.43e-02&-5.36e+00&6.14e-06\\
\hline
Confident Neighbor&Pref. Attach.&Small World&-4.49e-02&-7.20e+00&7.03e-11\\
Confident Neighbor&Pref. Attach.&Long Path&-5.03e-03&-7.65e-01&2.67e+01\\
Confident Neighbor&Pref. Attach.&Random Pod&2.61e-02&4.02e+00&3.74e-03\\
Confident Neighbor&Small World&Pref. Attach.&4.49e-02&7.20e+00&7.03e-11\\
Confident Neighbor&Small World&Long Path&3.99e-02&6.96e+00&3.80e-10\\
Confident Neighbor&Small World&Random Pod&7.10e-02&1.18e+01&1.98e-28\\
Confident Neighbor&Long Path&Pref. Attach.&5.03e-03&7.65e-01&2.67e+01\\
Confident Neighbor&Long Path&Small World&-3.99e-02&-6.96e+00&3.80e-10\\
Confident Neighbor&Long Path&Random Pod&3.11e-02&4.89e+00&7.03e-05\\
Confident Neighbor&Random Pod&Pref. Attach.&-2.61e-02&-4.02e+00&3.74e-03\\
Confident Neighbor&Random Pod&Small World&-7.10e-02&-1.18e+01&1.98e-28\\
Confident Neighbor&Random Pod&Long Path&-3.11e-02&-4.89e+00&7.03e-05\\
\hline
Conform&Pref. Attach.&Small World&3.67e-02&6.85e+00&7.73e-10\\
Conform&Pref. Attach.&Long Path&-1.73e-01&-2.40e+01&7.10e-99\\
Conform&Pref. Attach.&Random Pod&-2.77e-01&-4.08e+01&6.29e-213\\
Conform&Small World&Pref. Attach.&-3.67e-02&-6.85e+00&7.73e-10\\
Conform&Small World&Long Path&-2.09e-01&-3.46e+01&3.46e-171\\
Conform&Small World&Random Pod&-3.14e-01&-5.68e+01&1.63e-313\\
Conform&Long Path&Pref. Attach.&1.73e-01&2.40e+01&7.10e-99\\
Conform&Long Path&Small World&2.09e-01&3.46e+01&3.46e-171\\
Conform&Long Path&Random Pod&-1.04e-01&-1.43e+01&8.55e-41\\
Conform&Random Pod&Pref. Attach.&2.77e-01&4.08e+01&6.29e-213\\
Conform&Random Pod&Small World&3.14e-01&5.68e+01&1.63e-313\\
Conform&Random Pod&Long Path&1.04e-01&1.43e+01&8.55e-41\\
    \hline
    \end{tabular}
    \caption{Two-tailed paired t-values across networks, within strategies. Results are for parallel individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}

\begin{table*}[]
    \label{tab:t-innet-parallel}
    \centering
    \begin{tabular}{l|ll|ccc}
        Network & Strategy A & Strategy B & $\overline{B - A}$ & t & p* \\
    \hline
Pref. Attach.&Best Neighbor&Confident Neighbor&-3.78e-02&-5.94e+00&2.39e-07\\
Pref. Attach.&Best Neighbor&Conform&2.00e-01&2.77e+01&3.28e-124\\
Pref. Attach.&Confident Neighbor&Best Neighbor&3.78e-02&5.94e+00&2.39e-07\\
Pref. Attach.&Confident Neighbor&Conform&2.38e-01&3.40e+01&1.67e-167\\
Pref. Attach.&Conform&Best Neighbor&-2.00e-01&-2.77e+01&3.28e-124\\
Pref. Attach.&Conform&Confident Neighbor&-2.38e-01&-3.40e+01&1.67e-167\\
\hline
Small World&Best Neighbor&Confident Neighbor&-1.52e-02&-2.74e+00&3.80e-01\\
Small World&Best Neighbor&Conform&3.05e-01&5.30e+01&1.25e-290\\
Small World&Confident Neighbor&Best Neighbor&1.52e-02&2.74e+00&3.80e-01\\
Small World&Confident Neighbor&Conform&3.20e-01&5.89e+01&0.00e+00\\
Small World&Conform&Best Neighbor&-3.05e-01&-5.30e+01&1.25e-290\\
Small World&Conform&Confident Neighbor&-3.20e-01&-5.89e+01&0.00e+00\\
\hline
Long Path&Best Neighbor&Confident Neighbor&-3.88e-04&-6.64e-02&5.68e+01\\
Long Path&Best Neighbor&Conform&7.02e-02&9.34e+00&3.64e-18\\
Long Path&Confident Neighbor&Best Neighbor&3.88e-04&6.64e-02&5.68e+01\\
Long Path&Confident Neighbor&Conform&7.06e-02&9.15e+00&1.83e-17\\
Long Path&Conform&Best Neighbor&-7.02e-02&-9.34e+00&3.64e-18\\
Long Path&Conform&Confident Neighbor&-7.06e-02&-9.15e+00&1.83e-17\\
\hline
Random Pod&Best Neighbor&Confident Neighbor&-3.59e-03&-5.46e-01&3.51e+01\\
Random Pod&Best Neighbor&Conform&-6.84e-02&-9.54e+00&6.11e-19\\
Random Pod&Confident Neighbor&Best Neighbor&3.59e-03&5.46e-01&3.51e+01\\
Random Pod&Confident Neighbor&Conform&-6.48e-02&-8.96e+00&9.43e-17\\
Random Pod&Conform&Best Neighbor&6.84e-02&9.54e+00&6.11e-19\\
Random Pod&Conform&Confident Neighbor&6.48e-02&8.96e+00&9.43e-17\\
    \hline
    \end{tabular}
    \caption{Two-tailed paired t-values across strategies, within networks. Results are for parallel individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}
